\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2015-12-06 write_up/cricket.tex
home side toss

We assume that the outcome of a toss is random. Conditional on the outcome of a toss being random, the effect of winning a toss can be attributed to the toss itself. We begin by assessing the validity of the assumption. In particular, we assess whether teams win more tosses in their home country than outside.

>>>>

We assume that the outcome of a toss is random. Conditional on the outcome of a toss being random, the effect of winning the toss can be attributed to the toss itself. Before we exploit the design, we shed some light on the validity of the assumption. In particular, we assess whether the coin toss is somehow rigged, with home sides winning tosses more often. For this task, we limited ourselves to only international matches as establishing which of the teams is the home team in local matches is somewhat arduous. Of the 4,749 international matches, the home team won the toss in 2,433 matches, or about 51.2\%. The probability that we will get as large a proportion by chance after tossing close to 5,000 coins is about 9\%, low but not eyebrow-raisingly so.
